cardinalR: Generating interesting high-dimensional data structures

### 2025-08-22 paper-cardinalR.tex
Added more detailed figure titles

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-cubehole-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `gridcube`, `unifcube`, and `cubehole` data.}\label{fig:fig-cubehole-proj}
\end{figure}

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-cubic-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `quadratic` and `cubic` data.}\label{fig:fig-cubic-proj}
\end{figure}

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-pyrholes-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `pyrrect`, `pyrtri`, `pyrstar`, and `pyrholes` data.}\label{fig:fig-pyrholes-proj}
\end{figure}

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-scurve-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `scurve` and `scurvehole` data.}\label{fig:fig-scurve-proj}
\end{figure}

@@

{\centering \includegraphics[width=0.8\linewidth]{paper-cardinalR_files/figure-latex/fig-hemisphere-proj-1}

@@

\caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `circle`, `curvycycle`, `unifsphere`, `gridedsphere`, `clusteredspheres`, and `hemisphere` data.}\label{fig:fig-hemisphere-proj}
\end{figure}

@@

\caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `crescent`, `curvycylinder`, `sphericalspiral`, `helicalspiral`, `conicspiral`, and `nonlinear` data.}\label{fig:fig-triginometric-proj}
\end{figure}

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-trefoil-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `trefoil4d` and `trefoil3d` data.}\label{fig:fig-trefoil-proj}
\end{figure}

>>>>

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-cube-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `gridcube` (a1-a3), `unifcube` (b1-b3), and `cubehole` (c1-c3) data.}\label{fig:fig-cube-proj}
\end{figure}

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-cubic-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `quadratic` (a1-a3) and `cubic` (b1-b3) data.}\label{fig:fig-cubic-proj}
\end{figure}

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-pyr-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `pyrrect` (a1-a3), `pyrtri` (b1-b3), `pyrstar` (c1-c3), and `pyrholes` (d1-d3) data.}\label{fig:fig-pyr-proj}
\end{figure}

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-scurve-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `scurve` (a1-a3) and `scurvehole` (b1-b3) data.}\label{fig:fig-scurve-proj}
\end{figure}

@@

{\centering \includegraphics[width=0.8\linewidth]{paper-cardinalR_files/figure-latex/fig-sphere-proj-1}

@@

\caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `circle` (a1-a3), `curvycycle` (b1-b3), `unifsphere` (c1-c3), `gridedsphere` (d1-d3), `clusteredspheres` (e1-e3), and `hemisphere` (f1-f3) data.}\label{fig:fig-sphere-proj}
\end{figure}

@@

\caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `crescent` (a1-a3), `curvycylinder` (b1-b3), `sphericalspiral` (c1-c3), `helicalspiral` (d1-d3), `conicspiral` (e1-e3), and `nonlinear` (f1-f3) data.}\label{fig:fig-triginometric-proj}
\end{figure}

@@

\begin{figure}[!]
\includegraphics[width=1\linewidth]{paper-cardinalR_files/figure-latex/fig-trefoil-proj-1} \caption{Three $2\text{-}D$ projections from $4\text{-}D$, for the `trefoil4d` (a1-a3) and `trefoil3d` (b1-b3) data.}\label{fig:fig-trefoil-proj}
\end{figure}
